---
title: "Cancer_Genomics_Data_Challenge"
author: "Stephen Guest"
date: "Friday, August 21, 2015"
output: html_document
---

I am attempting to put together a 'data challenge' for the Charleston Data Analyticis group.  My idea is to assemble genomics data for a group of cell lines that have been treated with Navitoclax and an IC50 value determined.  I will then provide the group with the genomics data and the IC50 value for each cell line and ask them to develop a classifier that could predict the IC50 value for a new cell line given the genomics data for that cell line

In order to get navitoclax IC50 data I am first using the Broad Institute Cancer Therapeutics Data Portal at

https://ctd2.nci.nih.gov/dataPortal/

on 08/21/15 I downloaded the raw data for the "Identifying and Targeting Cancer Dependencies With Small Molecules" project.  The file of interest in this batch of files is:  Broad.CTD2.D3.area_under_conc_curve

Note that on 12/18/15 I was unable to find this file in the above location.  There is however a new dataset available

Reading in the data file from my local directory and pulling out only the data for navitoclax


```{r}
setwd("C:/Users/stg43/Charleston Data Analytics/Cancer Genomics Data Challenge")
ctdp<-read.table("Broad.CTD2.D3.area_under_conc_curve.txt", sep="\t", header=T)
nav<-ctdp[ctdp$compound_name=="navitoclax",]
```

Next we'll rename some of the nav dataframe columns and generate a z score for the response metric variable

```{r}
nav<-nav[,-2]
names(nav)<-c("tumorID","response_metric_AUC")
nav$Z_score<-scale(nav$response_metric_AUC, center=T, scale=T)
```

There are also some cell lines that appear more than once in the nav data sest.  I do not know why this is.  Perhaps different culture conditions?  Really don't know. Should probably investigate this further but in the interest of time I will delete the extra occurences of the duplicated cell lines

```{r}
x<-duplicated(nav$tumorID)
nav<-nav[!x,]
```

This data can now be merged with the CCLE genomic data sets based on the tumorID variable