---
title: "Results (Iteration 1)"
author: Eric Czech
output: html_document
#output: ioslides_presentation
widescreen: yes
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
knit: (function(inputFile, encoding) { rmarkdown::render(
        inputFile, encoding=encoding, 
        output_file=file.path(dirname(inputFile), 'pres_01_output', 'cosmic', 'pres.doc.html')) })
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(root.dir = '~/repos/musc_genomics/src/R/main/data_pres/test')
setwd('~/repos/musc_genomics/src/R/main')
source('data_model/training_viz.R')
lib('plotly')
RESPONSE_TYPE <- 'cosmic'
cache <- Cache(dir=file.path(CACHE_DIR, 'result_data'), project=RESPONSE_TYPE)

cv.res <- cache$get('cv_model_perf')
ho.res <- cache$get('ho_model_perf')

p.fold.roc <- PlotPerFoldROC(cv.res)
p.cv.roc <- PlotAllFoldROC(cv.res) %>% ggplotly() %>% layout(showlegend = T) %>% plot.ly
p.ho.roc <- PlotHoldOutROC(ho.res) %>% ggplotly() %>% layout(showlegend = T) %>% plot.ly

d.res <- cache$get('response_data')
p.res.dist <- PlotResponseDist(RESPONSE_TYPE, d.res)

p.cv.auc <- PlotFoldMetric(cv.res, 'auc') + ylim(.4, .9)
p.ho.auc <- PlotHoldOutMetric(ho.res, 'auc') + ylim(.4, .9)

p.cv.acc <- PlotFoldMetric(cv.res, 'acc.max') + ylim(.6, .8)
p.ho.acc <- PlotHoldOutMetric(ho.res, 'acc.max') + ylim(.6, .8)

```

<br><br>
<hr>

# Classification Results

## Models Considered {.smaller}

Models tried so far:

- ElasticNet (+ ridge/lasso)
- SVM (radial)
- PAM aka "Predictive Analysis for Microarrays" (basically shrunken centroids)
- kNN (also w/ PCA preprocessing)
- Partial Least Squares
- Random Forest

In the works:

- [SCRDA](https://web.stanford.edu/~hastie/Papers/RDA-6.pdf) - This looks promising
- RDA (a simpler version of the above)
- GBM / ExtraTrees

## Data Prep and Partitioning {.smaller}

- So far, only COSMIC ic 50 scores used as a response (gives 410 observations with 36,791 features)
- Only mutations that occur at least 3 times used
- Training set created as random sample of size N * .8
- Hold out set was remaining 20% of sample
- To run classification, response split at mean; response distribution:

```{r, echo=FALSE, fig.align='center', fig.width=4, fig.height=4}
p.res.dist
```

## CV Results (ROC)

ROC curves across models and folds on training data: 

```{r, echo=FALSE, fig.align='center', fig.width=10, fig.height=8}
p.fold.roc
```

## CV ROC (combined) {.smaller} 

ROC curves combined across folds (should resemble holdout ROC):

```{r, echo=FALSE, fig.align='center', fig.width=9, fig.height=5}
p.cv.roc
```

## Holdout ROC {.smaller}

ROC curves by model on hold out data:

```{r, echo=FALSE, fig.align='center', fig.width=9, fig.height=5}
p.ho.roc
```

## Accuracy Summary

```{r, echo=FALSE, fig.align='center', fig.width=8, fig.height=3}
p.cv.acc
p.ho.acc
```

## AUC Summary

```{r, echo=FALSE, fig.align='center', fig.width=8, fig.height=3}
p.cv.auc
p.ho.auc
```