---
title: "Results (Iteration 2)"
author: Eric Czech
output: html_document
#output: ioslides_presentation
widescreen: yes
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
knit: (function(inputFile, encoding) { rmarkdown::render(
        inputFile, encoding=encoding, 
        output_file=file.path(dirname(inputFile), 'pres_02_output', 'cosmic', 'pres.doc.html')) })
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(knitr)
opts_chunk$set(root.dir = '~/repos/musc_genomics/src/R/main/data_pres/test')
setwd('~/repos/musc_genomics/src/R/main')
source('data_model/training_viz.R')
lib('plotly')

# When changing the response type, make sure to also change the output
# directory in the "knit" function setting in header

RESPONSE_TYPE <- 'cosmic'
RESPONSE_SELECTOR <- function(d){d %>% filter(!is.na(ic_50)) %>% rename(response=ic_50) %>% select(-auc)}
RESPONSE_THRESH <- -1

# RESPONSE_TYPE <- 'ctd'
# RESPONSE_SELECTOR <- function(d){d %>% filter(!is.na(auc)) %>% rename(response=auc) %>% select(-ic_50)}
# RESPONSE_THRESH <- -1

cache <- Cache(dir=file.path(CACHE_DIR, 'result_data'), project=RESPONSE_TYPE)

d.prep <- GetTrainingData(TRAIN_CACHE, RESPONSE_TYPE, RESPONSE_SELECTOR, min.mutations=3)


cv.res <- cache$get('cv_model_perf')
ho.res <- cache$get('ho_model_perf')

cb.acc.rec <- cache$get('cb_acc_rec')
ho.acc.rec <- cache$get('ho_acc_rec')

p.fold.roc <- PlotPerFoldROC(cv.res)
p.cv.roc <- PlotAllFoldROC(cv.res) %>% ggplotly() %>% layout(showlegend = T) %>% plot.ly
p.ho.roc <- PlotHoldOutROC(ho.res) %>% ggplotly() %>% layout(showlegend = T) %>% plot.ly

d.res <- cache$get('response_data')
p.res.dist <- PlotResponseDist(RESPONSE_TYPE, d.res, response.cutoff=-1)

y <- DichotomizeOutcome(d.prep[,'response'], RESPONSE_THRESH)
y.cache <- DichotomizeOutcome(d.res, RESPONSE_THRESH)
if (!all(y == y.cache)) stop('Cached response not equal to inferred response')

p.cv.cm <- PlotFoldConfusion(cv.res)
p.ho.cm <- PlotHoldOutConfusion(ho.res)

p.cv.kappa <- PlotFoldMetric(cv.res, 'kappa')
p.cv.acc <- PlotFoldMetric(cv.res, 'acc')
p.ho.kappa <- PlotHoldOutMetric(ho.res, 'kappa')# + ylim(.4, .9)
p.ho.acc <- PlotHoldOutMetric(ho.res, 'acc')
```

<br>

<center><h1>
```{r, results='asis', echo=FALSE}
cat(RESPONSE_TYPE)
```
 Classification Results</h1></center>
<hr>

## Data Summary

Original dataset dimensions: 
```{r, results='asis', echo=FALSE}
dim(d.prep)
```

Response was standardized and split at -1.  Response frequency:
```{r, echo=FALSE}
table(y)
```

No Information Rate (this is the accuracy to beat) = 
```{r, echo=FALSE, results='asis'}
cat(max(table(y))/length(y))
```

Data was split 3-ways into 50% training, 33% holdout, and 17% calibration

## Kappa Performance

Kappa values across 3 times repeated 10-fold CV:

```{r, echo=FALSE, fig.align='center', fig.width=10, fig.height=5}
p.cv.kappa
```

Kappa values on holdout:

```{r, echo=FALSE, fig.align='center', fig.width=10, fig.height=5}
p.ho.kappa
```

## Accuracy Performance

Accuracy across 3 times repeated 10-fold CV:

```{r, echo=FALSE, fig.align='center', fig.width=10, fig.height=5}
p.cv.acc
```

Accuracy on holdout:

```{r, echo=FALSE, fig.align='center', fig.width=10, fig.height=5}
p.ho.acc
```

## Predictions with Probability Window

Predictive accuracy when allowing an upper and lower boundary on probability predictions (this leads to some cases being classified as 'na' or 'unsure'):

```{r, echo=FALSE}
knitr::kable(head(cb.acc.rec, 25))
```

Accuracy results when applying a window on predictions of [.4, .6]:

```{r, echo=FALSE}
knitr::kable(ho.acc.rec)
```

## A few Important Features

```{r, echo=FALSE}
select.vars <- c('ge.ITGB5', 'ge.YAP1', 'ge.ANXA2', 'ge.LMNA', 'ge.ITPRIPL2', 'ge.MYOF')
X <- d.prep[,select.vars]
X$response <- y
melt(X, id.vars='response') %>% 
  ggplot(aes(x=response, y=value)) + 
  geom_boxplot(outlier.size=0) +
  geom_jitter(alpha=.2, width=.3) + 
  facet_wrap(~variable, scales='free') + theme_bw()
```
