---
title: "CTD2 Versions"
output: html_document
---

The AUC file I used for the V1 data was ```v10.D3.area_under_conc_curve.txt``` and it came from this zip archive: [CTRPv1.0_2013_pub_Cell_154_1151.zip](ftp://caftpd.nci.nih.gov/pub/dcc_ctd2/Broad/CTRPv1.0_2013_pub_Cell_154_1151/CTRPv1.0_2013_pub_Cell_154_1151.zip)

The AUC file I used for the V2 data was ```v20.data.curves_post_qc.txt``` (joined with several meta data files) and it came from this zip archive: [CTRPv2.0_2015_ctd2_ExpandedDataset.zip](ftp://caftpd.nci.nih.gov/pub/dcc_ctd2/Broad/CTRPv2.0_2015_ctd2_ExpandedDataset/CTRPv2.0_2015_ctd2_ExpandedDataset.zip)


```{r, echo=F, message=FALSE, error=FALSE, warning=FALSE}
library(stringr)
library(tidyr)
library(ggplot2)
setwd('~/repos/musc_genomics/src/R/main')
source('utils.R')
source('data_import/import_lib.R')
# dt %>% mutate_each(funs(is.na), starts_with('auc')) %>% 
#   unite(auc, auc_v1, auc_v2) %>% .$auc %>% table
```

### Joining both datasets

```{r, echo=T}
d1 <- GetCTD2V1Data() %>% rename(auc_v1=area_under_curve) 
d2 <- GetCTD2V2Data() %>% rename(auc_v2=area_under_curve)
cbind(head(d1), head(d2))
```

```{r, echo=T}
# Compute differences in AUC values
dt <- d1 %>% full_join(d2, by='tumor_id') %>% mutate(diff_auc=auc_v1 - auc_v2)

# Determine cell line IDs only in each dataset
only.v1 <- subset(dt, is.na(auc_v2)) %>% .$tumor_id %>% unique %>% sort
only.v2 <- subset(dt, is.na(auc_v1)) %>% .$tumor_id %>% unique %>% sort

print(paste0('Number of records in joined dataset:', nrow(dt)))
```

### AUC Differences

AUC values in V1 vs V2:
```{r, warning=FALSE}
dt %>% ggplot(aes(x=auc_v1, y=auc_v2)) + geom_point() + theme_bw() + 
  xlab('V1 Value') + ylab('V2 Value')
```

AUC difference density and summary:
```{r, warning=FALSE}
summary(dt$diff_auc)
dt %>% ggplot(aes(x=diff_auc)) + geom_density() + theme_bw()
```

### Version One Data

```{r, echo=F}
print(paste0('Number of Cell Lines only in V1 data: ', length(only.v1)))
print('Cell Lines only in V1 data:')
only.v1
```

### Version Two Data

```{r, echo=F}
print(paste0('Number of Cell Lines only in V2 data: ', length(only.v2)))
print('Cell Lines only in V2 data:')
only.v2
```

